Operational Feature Selection with Gaussian Mixture Models for remote sensing images

### 2016-10-07 paper.tex
complete tab

    \begin{table}[!t]
        \centering
        \caption{Kappa coefficient and processing time for 1,000 samples by class and averaged over 5 trials (standard deviation in parenthesis). Processing times are given in second.\label{tab:potsdam-otbsimu}}
        \begin{tabular}{lcccccc}\toprule
            & {\bfseries 5\_11 (train)} & {\bfseries 5\_12 (test)} & {\bfseries 3\_10 (test)} & {\bfseries Train. Time} & {\bfseries Classif. time} & {\bfseries \# of selected features} \\ \cline{2-7}
            GMM SFS kappa & 0.694 (0.002)             & {\bfseries 0.669 (0.005)} & {\bfseries 0.533 (0.008)} & 400 & 310  & 13.2 \\
            GMM SFS JM &    0.624 (0.028)             & 0.631 (0.034)             & 0.461 (0.027)             & 2   & 310  & 11 \\
            GMM SFFS JM &   0.624 (0.028)             & 0.631 (0.034)             & 0.461 (0.027)             & 2.6 & 310  & 11 \\
            GMM ridge &     0.632 (0.007)             & 0.592 (0.010)             & 0.433 (0.008)             & 10  & 2000 & all \\
            KNN &           0.637 (0.005)             & 0.607 (0.005)             & 0.478 (0.002)             &     &      & all \\
            Random Forest & {\bfseries 0.729 (0.004)} & {\bfseries 0.673 (0.005)} & {\bfseries 0.529 (0.009)} & 20  & 840  & all \\
            \bottomrule
        \end{tabular}
    \end{table}

>>>>

    \begin{table}[!t]
        \centering
        \caption{Kappa coefficient and processing time for 1,000 samples by class and averaged over 5 trials (standard deviation in parenthesis). Processing times are given in second.\label{tab:potsdam-otbsimu}}
        \begin{tabular}{lcccccc}\toprule
            & {\bfseries 5\_11 (train)} & {\bfseries 5\_12 (test)} & {\bfseries 3\_10 (test)} & {\bfseries Train. Time} & {\bfseries Classif. time} & {\bfseries \# of selected features} \\ \cline{2-7}
            GMM SFS kappa & 0.694 (0.002)             & {\bfseries 0.669 (0.005)} & {\bfseries 0.533 (0.008)} & 400 & 310  & 13.2 \\
            GMM SFS JM &    0.624 (0.028)             & 0.631 (0.034)             & 0.461 (0.027)             & 2   & 310  & 11 \\
            GMM SFFS JM &   0.624 (0.028)             & 0.631 (0.034)             & 0.461 (0.027)             & 2.6 & 310  & 11 \\
            GMM ridge &     0.632 (0.007)             & 0.592 (0.010)             & 0.433 (0.008)             & 10  & 2000 & all \\
            KNN &           0.637 (0.005)             & 0.607 (0.005)             & 0.478 (0.002)             & 0.7 & 9500 & all \\
            Random Forest & {\bfseries 0.729 (0.004)} & {\bfseries 0.673 (0.005)} & {\bfseries 0.529 (0.009)} & 20  & 840  & all \\
            \bottomrule
        \end{tabular}
    \end{table}
